A quantitative framework for investigating the reliability of empirical network construction: supplemental information

### 2019-01-17 manuscript/supplemental.tex
SI ready

  \begin{figure}
  \label{sim_props}
  \caption{We created 100 random networks containing 50 consumers and 50 resources, with a connectance of 0.1. For each of these ``original" networks, we created 100 process-filtered (``process") networks incorporating uncertainty around the occurrence of each interaction during sampling. For each ``process" network, we further created 100 detection-filtered (``detection") networks incorporating uncertainty around the detection of each interaction. For each network, we show the mean (+/- SD) connectance, links per consumer, nestedness (NODF), and links per resource.}
  \begin{center}
  \includegraphics*[width=.9\textwidth]{figures/simulation_example.eps}
  \end{center}
  \end{figure}

@@

  \begin{table}
  \caption{Attributions for silhouette images taken from PhyloPic.org and used in Figure 1 (\emph{main text}). Terms for the CC BY-NC-SA 3.0 license can be found at \emph{https://creativecommons.org/licenses/by-nc-sa/3.0/}. Terms for the CC BY 3.0 license can be found at \emph{https://creativecommons.org/licenses/by/3.0/}.}
  \begin{tabular}{l|l m{10cm}}
  Image & PhyloPic taxon & Attribution \\
  \hline
  Lion & Panthera leo & Public domain (uncredited) \\
  Leopard & Panthera pardus & Lukasiniho (CC BY-NC-SA 3.0; image not changed) \\
  Jackal & Canidae & Brian Gratwicke (photo) and T. Michael Keesey (vectorization). (CC BY 3.0; image not changed) \\
  Elephant & Loxodonta africana & Jan A. Venter, Herbert H. T. Prins, David A. Balfour \& Rob Slotow (vectorized by T. Michael Keesey) (CC BY 3.0; image not changed) \\
  Zebra & Equus quagga & Cathy (CC BY-NC-SA 3.0; image not changed) \\
  Impala & Aepyceros melampus & Public domain (unknown author) \\
  Hare & Leporidae & Sarah Werning (CC A 3.0; image not changed) \\
  Acacia & Acacia & Mattia Menchetti (public domain) \\
  Grass & & Not sourced from PhyloPic. Public domain. \\
  \hline
  \end{tabular}
  \end{table}

@@

        \begin{figure}[h!]
          \caption{Imperfect detection of interactions increases the number of samples required to be confident that an interaction never occurs. Assume that two species cannot interact (i.e., $\lambda=0$) and that the number of observed interactions follows a binomial distribution depending upon the number of observed interactions $k$ and observed co-occurrances $n$. The maximum likelihood estimate (MLE) for $\lambda_{ij}$ is $\lambda_{MLE}=\frac{k}{n}$. Note that $\lambda_{ij}$ is not a point estimate but rather a random variable with an unknown distribution. This means that if $k = 0$ in a given sample, this does not necessarily imply that the two species will never interact. Rather, $k = 0$ implies that `no interaction' is the most likely outcome when the species do co-occur but there is nonetheless some chance that the two species \emph{could} interact.\\
          Importantly, we can estimate the variance of $\lambda_{ij}$ as well as the MLE; available methods include the \emph{Wilson score interval}, the \emph{Clopper-Pearson interval}, and the \emph{Agresti-Coull interval} (for details, see [\citealp{Brown2001}]). The distribution of the MLE for $\lambda_{ij}$ thus obtained is a key part of the Bayesian distribution for $\lambda_{ij}$.
          Here we show the upper bound (solid black line) of a 95\% Clopper-Pearson true credible interval for the interaction probability $\lambda_{ij}$ for a pair of species that has been observed co-occurring $n$ times but never interacting ($k = 0$). The upper limit of the credible interval only reaches 0.1 (dashed, red line) with 35 observations. Thus, adding more observations is useful in controlling uncertainty, but the number of observations added must be very high unless we have some other reason to believe that an interaction cannot occur (i.e., a strong prior).}
          \label{upper_limits}
          \begin{center}
          % \includegraphics*[width=.8\textwidth]{figures/upper_limit_DG.eps}
          % \includegraphics*[width=.8\textwidth]{Figure_3.eps}
          \end{center}
          \end{figure}

@@

    %   It is common to perform analyses that require calculating higher-order network properties in interaction networks. The fact that the posterior distribution of $\lambda$ follows a beta distribution makes it straightforward to compute moments and other properties needed for these analyses.

    %   The \textbf{average} of $\lambda$ is: 
    %       \begin{equation}
    %         \bar{\lambda} = \frac{\alpha+k}{\alpha+\beta+n} ,
    %         \label{mean}
    %       \end{equation}

    %     and its \textbf{variance} is:  
    %       \begin{equation}
    %         Var(\lambda|k) = \frac{(\alpha + k)(\beta + n - k)}{(\alpha + \beta + n)^{2}(\alpha + \beta + n +1)}
    %         \label{variance}
    %       \end{equation}

    %     The \textbf{mode} of the distribution is:
    %       \begin{equation}
    %         \hat{\lambda} = \frac{\alpha + k - 1}{\alpha + \beta + n - 2} .
    %         \label{mode}
    %       \end{equation}

@@

  \begin{figure}[h!]
    \caption{Mean connectance, links per galler, nestedness (NODF), and links per natural enemy for networks assembled using posterior distributions based on a single site (Zillis in Graub\"{u}nden, Switzerland) from~\citet{Kopelke2017} occupied a narrow range. To obtain distributions of network properties, we created 100 ``posterior-sampling" networks and then, for each of these, created 100 ``filtered" networks by randomly sampling 50\%-99\% of the interactions included in the posterior-sampling network. This simulates imperfect detection of interactions in the field. Each point represents the mean (+/- SD) network property (e.g., connectance) obtained from a set of 100 filtered networks. The filtered networks cover a broader range of network properties than the posterior-sampling networks but the value of each property decreases as the strength of the detection filter increases. Values in the original web are indicated by dashed lines.}
    \label{posterior_webs}    
    \begin{center}
    % \includegraphics[width=.8\textwidth]{figures/GP_posterior_properties_Zillis.eps}
    % \includegraphics[width=.8\textwidth]{Figure_5.eps}
    \end{center}
    \end{figure}

@@

      % % # R code to make the table:
      % ns=c(0,1,2,5,10,15,20,25,50,100,150,200,374)
      % output=matrix(nrow=length(ns),ncol=5)
      % output[,1]=ns
      % for(r in 1:nrow(output)){
      %   interval1=credible_interval(calculate_parameters(sg_int_probs,ns[r],0),0.025,0.975)    
      %   interval2=credible_interval(calculate_parameters(gp_int_probs,ns[r],0),0.025,0.975)    
      %   output[r,2:3]=interval1
      %   output[r,4:5]=interval2
      % }
      \medskip
      \begin{table}
        \label{credints}
        \caption{Here we give the lower and upper bounds of 95\% credible intervals for the probability of interaction $\lambda$ between \emph{Salix}-galler or galler-natural enemy pairs that have been observed co-occurring $n$ times but have never been observed interacting.}
        \begin{tabular}{l  c c  c c }
        \multirow{2}{*}{$n$} & \multicolumn{2}{c}{\emph{Salix}-galler} & \multicolumn{2}{c}{galler-natural enemy}\\
         & Lower bound & Upper bound & Lower bound & Upper bound \\
        \hline
        0   & 0.013 & 0.049 & 5.39 $\times10^{-4}$ & 0.304 \\
        1   & 0.013 & 0.048 & 4.82 $\times10^{-4}$ & 0.276 \\
        2   & 0.013 & 0.048 & 4.35 $\times10^{-4}$ & 0.253 \\
        5   & 0.012 & 0.048 & 3.37 $\times10^{-4}$ & 0.203 \\
        10  & 0.012 & 0.047 & 2.45 $\times10^{-4}$ & 0.152 \\
        15  & 0.012 & 0.046 & 1.93 $\times10^{-4}$ & 0.121 \\
        20  & 0.012 & 0.046 & 1.59 $\times10^{-4}$ & 0.101 \\
        25  & 0.012 & 0.045 & 1.35 $\times10^{-4}$ & 0.087 \\
        50  & 0.011 & 0.042 & 7.72 $\times10^{-5}$ & 0.050 \\
        100 & 0.010 & 0.037 & 4.16 $\times10^{-5}$ & 0.027 \\
        150 & 0.009 & 0.033 & 2.84 $\times10^{-5}$ & 0.019 \\
        200 & 0.008 & 0.030 & 2.16 $\times10^{-5}$ & 0.014 \\
        \hline
        374 & 0.006 & 0.022 & 1.18 $\times10^{-5}$ & 0.008 \\
        \hline
        \end{tabular}
      \end{table}

>>>>

  \begin{figure}
  \caption{We created 100 random networks containing 50 consumers and 50 resources, with a connectance of 0.1. For each of these ``original" networks, we created 100 process-filtered (``process") networks incorporating uncertainty around the occurrence of each interaction during sampling. For each ``process" network, we further created 100 detection-filtered (``detection") networks incorporating uncertainty around the detection of each interaction. For each network, we show the mean (+/- SD) connectance, links per consumer, nestedness (NODF), and links per resource.}
  \label{sim_props}
  \begin{center}
  \includegraphics*[width=.9\textwidth]{figures/simulation_example.eps}
  \end{center}
  \end{figure}

@@

  \begin{table}[h!]
  \caption{Attributions for silhouette images taken from PhyloPic.org and used in Figure 1 (\emph{main text}). Terms for the CC BY-NC-SA 3.0 license can be found at \emph{https://creativecommons.org/licenses/by-nc-sa/3.0/}. Terms for the CC BY 3.0 license can be found at \emph{https://creativecommons.org/licenses/by/3.0/}.}
  \begin{tabular}{l|l m{10cm}}
  Image & PhyloPic taxon & Attribution \\
  \hline
  Lion & Panthera leo & Public domain (uncredited) \\
  Leopard & Panthera pardus & Lukasiniho (CC BY-NC-SA 3.0; image not changed) \\
  Jackal & Canidae & Brian Gratwicke (photo) and T. Michael Keesey (vectorization). (CC BY 3.0; image not changed) \\
  Elephant & Loxodonta africana & Jan A. Venter, Herbert H. T. Prins, David A. Balfour \& Rob Slotow (vectorized by T. Michael Keesey) (CC BY 3.0; image not changed) \\
  Zebra & Equus quagga & Cathy (CC BY-NC-SA 3.0; image not changed) \\
  Impala & Aepyceros melampus & Public domain (unknown author) \\
  Hare & Leporidae & Sarah Werning (CC A 3.0; image not changed) \\
  Acacia & Acacia & Mattia Menchetti (public domain) \\
  Grass & & Not sourced from PhyloPic. Public domain. \\
  \hline
  \end{tabular}
  \end{table}

@@

        \begin{figure}[h!]
          \caption{Imperfect detection of interactions increases the number of samples required to be confident that an interaction never occurs. Assume that two species cannot interact (i.e., $\lambda=0$) and that the number of observed interactions follows a binomial distribution depending upon the number of observed interactions $k$ and observed co-occurrances $n$. The maximum likelihood estimate (MLE) for $\lambda_{ij}$ is $\lambda_{MLE}=\frac{k}{n}$. Note that $\lambda_{ij}$ is not a point estimate but rather a random variable with an unknown distribution. This means that if $k = 0$ in a given sample, this does not necessarily imply that the two species will never interact. Rather, $k = 0$ implies that `no interaction' is the most likely outcome when the species do co-occur but there is nonetheless some chance that the two species \emph{could} interact.\\
          Importantly, we can estimate the variance of $\lambda_{ij}$ as well as the MLE; available methods include the \emph{Wilson score interval}, the \emph{Clopper-Pearson interval}, and the \emph{Agresti-Coull interval} (for details, see [\citealp{Brown2001}]). The distribution of the MLE for $\lambda_{ij}$ thus obtained is a key part of the Bayesian distribution for $\lambda_{ij}$.
          Here we show the upper bound (solid black line) of a 95\% Clopper-Pearson true credible interval for the interaction probability $\lambda_{ij}$ for a pair of species that has been observed co-occurring $n$ times but never interacting ($k = 0$). The upper limit of the credible interval only reaches 0.1 (dashed, red line) with 35 observations. Thus, adding more observations is useful in controlling uncertainty, but the number of observations added must be very high unless we have some other reason to believe that an interaction cannot occur (i.e., a strong prior).}
          \label{upper_limits}
          \begin{center}
          \includegraphics*[width=.8\textwidth]{figures/upper_limit_DG.eps}
          % \includegraphics*[width=.8\textwidth]{Figure_3.eps}
          \end{center}
          \end{figure}

@@

      It is common to perform analyses that require calculating higher-order network properties in interaction networks. The fact that the posterior distribution of $\lambda$ follows a beta distribution makes it straightforward to compute moments and other properties needed for these analyses.

      The \textbf{average} of $\lambda$ is: 
          \begin{equation}
            \bar{\lambda} = \frac{\alpha+k}{\alpha+\beta+n} ,
            \label{mean}
          \end{equation}

        and its \textbf{variance} is:  
          \begin{equation}
            Var(\lambda|k) = \frac{(\alpha + k)(\beta + n - k)}{(\alpha + \beta + n)^{2}(\alpha + \beta + n +1)}
            \label{variance}
          \end{equation}

        The \textbf{mode} of the distribution is:
          \begin{equation}
            \hat{\lambda} = \frac{\alpha + k - 1}{\alpha + \beta + n - 2} .
            \label{mode}
          \end{equation}

@@

  \begin{figure}[h!]
    \caption{Mean connectance, links per galler, nestedness (NODF), and links per natural enemy for networks assembled using posterior distributions based on a single site (Zillis in Graub\"{u}nden, Switzerland) from~\citet{Kopelke2017} occupied a narrow range. To obtain distributions of network properties, we created 100 ``posterior-sampling" networks and then, for each of these, created 100 ``filtered" networks by randomly sampling 50\%-99\% of the interactions included in the posterior-sampling network. This simulates imperfect detection of interactions in the field. Each point represents the mean (+/- SD) network property (e.g., connectance) obtained from a set of 100 filtered networks. The filtered networks cover a broader range of network properties than the posterior-sampling networks but the value of each property decreases as the strength of the detection filter increases. Values in the original web are indicated by dashed lines.}
    \label{posterior_webs}    
    \begin{center}
    \includegraphics[width=.8\textwidth]{figures/GP_posterior_properties_Zillis.eps}
    % \includegraphics[width=.8\textwidth]{Figure_5.eps}
    \end{center}
    \end{figure}

\clearpage
\newpage

@@

      % % # R code to make the table:
      % ns=c(0,1,2,5,10,15,20,25,50,100,150,200,374)
      % output=matrix(nrow=length(ns),ncol=5)
      % output[,1]=ns
      % for(r in 1:nrow(output)){
      %   interval1=credible_interval(calculate_parameters(sg_int_probs,ns[r],0),0.025,0.975)    
      %   interval2=credible_interval(calculate_parameters(gp_int_probs,ns[r],0),0.025,0.975)    
      %   output[r,2:3]=interval1
      %   output[r,4:5]=interval2
      % }
      \medskip
      \begin{table}[h!]
        \label{credints}
        \caption{Here we give the lower and upper bounds of 95\% credible intervals for the probability of interaction $\lambda$ between \emph{Salix}-galler or galler-natural enemy pairs that have been observed co-occurring $n$ times but have never been observed interacting.}
        \begin{tabular}{l  c c  c c }
        \multirow{2}{*}{$n$} & \multicolumn{2}{c}{\emph{Salix}-galler} & \multicolumn{2}{c}{galler-natural enemy}\\
         & Lower bound & Upper bound & Lower bound & Upper bound \\
        \hline
        0   & 0.013 & 0.049 & 5.39 $\times10^{-4}$ & 0.304 \\
        1   & 0.013 & 0.048 & 4.82 $\times10^{-4}$ & 0.276 \\
        2   & 0.013 & 0.048 & 4.35 $\times10^{-4}$ & 0.253 \\
        5   & 0.012 & 0.048 & 3.37 $\times10^{-4}$ & 0.203 \\
        10  & 0.012 & 0.047 & 2.45 $\times10^{-4}$ & 0.152 \\
        15  & 0.012 & 0.046 & 1.93 $\times10^{-4}$ & 0.121 \\
        20  & 0.012 & 0.046 & 1.59 $\times10^{-4}$ & 0.101 \\
        25  & 0.012 & 0.045 & 1.35 $\times10^{-4}$ & 0.087 \\
        50  & 0.011 & 0.042 & 7.72 $\times10^{-5}$ & 0.050 \\
        100 & 0.010 & 0.037 & 4.16 $\times10^{-5}$ & 0.027 \\
        150 & 0.009 & 0.033 & 2.84 $\times10^{-5}$ & 0.019 \\
        200 & 0.008 & 0.030 & 2.16 $\times10^{-5}$ & 0.014 \\
        \hline
        374 & 0.006 & 0.022 & 1.18 $\times10^{-5}$ & 0.008 \\
        \hline
        \end{tabular}
      \end{table}
